\documentclass[14pt]{article}

\begin{document}

\begin{center}\begin{small} MAKERERE UNIVERSITY \end{small}\end{center}

\begin{center}\begin{small} COLLEGE OF COMPUTING AND INFORMATION SCIENCES \end{small}\end{center}

\begin{center}\begin{small} SCHOOL OF COMPUTING AND INFORMATION SCIENCES \end{small}\end{center}

\begin{center}\begin{small} DEPARTMENT OF COMPUTER SCIENCE \end{small}\end{center}

\begin{center}\begin{small} BACHELOR OF SCIENCE IN COMPUTER SCIENCE \end{small}\end{center}

\begin{center}\begin{small} COURSE NAME: RESEARCH METHODOLOGY \end{small}\end{center}

\begin{center}\begin{small} COURSE CODE: BIT 2207 \end{small}\end{center}

\begin{center}\begin{small} NAME: AMULEN SHARON ESTHER \end{small}\end{center}

\begin{center}\begin{small} REG NO: 15/U/3459/PS \end{small}\end{center}

\begin{center}\begin{small} STUD NO: 215015331 \end{small}\end{center}


\title{THE ART OF MAKING CAKES}

\maketitle

\section{SUMMARY}
Making cakes is quite a process which involves baking. It also involves many other ingredients put into the cake in order to produce a flavored and tasty result. The cake is put into the oven after the long processes that are involved for example the mixing and all the others and eventually it is removed from the oven and ready for tasting.

\section{BACKGROUNG}
The idea of making of cakes as a problem popped up because it is what I usually do in my free time apart from class work. So I decided to take it up as a problem for which I can easily provide the solutions for it. Cakes can be made in different flavors preferred by a particular person that is the client who you are making the cake for, for example there are vanilla essence, pineapple essence and so many others. Cakes are mostly used as a dessert .Most cases the cake is coated with either icing or butter to make it tastier and look more presentable.

\section{BODY}
Mixtures
The actual making of the cake requires some ingredients for example flour, sugar, eggs, baking powder, baking soda, blue band, black current fruits, lemon and some spices such as cinnamon, nutmeg, mixed spices to mention but a few .The process begins by measuring approximately 500g of sugar and blue band each. They are both mixed together in a bowl until the sugar crystals get dissolved into the blue band and then beat 15 eggs and whisk them and then pour into the mixture of blue band and sugar. After that, measure approximately 900g of flour and two tea spoonful of baking powder  and keep on folding within the mixture using a mingling stick until everything is fully mixed and black current fruits as well as lemon juice are added and then mixed gently. The climax of the mixing stage is the addition of the spices that is the cinnamon, nutmeg , mixed spices and the baking soda all having the same measurements that is to say two tea spoonful each.
Baking
 The next stage is the preparation for baking and in this stage saucepans can be used and for this case i need to use at least two saucepans. In each saucepan, I smear blue band at the bottom of the saucepans and then dust the saucepan with flour so that the mixture doesn’t stick to the sides of the saucepan. Then pour the mixture in the saucepans but not filling to the brim at least three quarter way. The saucepans are then put inside the oven for about fifteen to thirty minutes at a particular temperature and the oven should be tightly covered to prevent air from penetrating inside because the dough may fail to rise and hence the cake will not get ready. After the cake is ready, it is left to cool thoroughly and then shaped and jam is applied to help in the preservation. The next process after this is the icing of the cake which requires the egg white and the icing sugar which is mixed together until it is firm enough .The mixture is then rolled using a rolling pin and then it is put on the cake to fit perfectly. The final step is the designing of the cake and hence the cake is done.

\section{CONCLUSION}
The making of a cake was quite an interesting exercise and it provided room for learning new things and expounding on my knowledge of all the cake ingredients. 
However, it was quite a long and tedious exercise which required time and patience and accuracy most especially on the icing part which needed accuracy and the process was generally expensive that is to say in the purchasing of the ingredients.

\end{document}



